---
pagetitle: "Ninja knitting with Star Wars"
output:
  xaringan::moon_reader:
    css: ["default", "styles/custom.css", "styles/custom-fonts.css"]
    seal: false
    lib_dir: libs
    self_contained: true
    nature:
      countIncrementalSlides: false
params: 
  name: NULL

---
layout: true

```{r setup, include=FALSE}
# Load packages
library(dplyr)
library(ggplot2)
library(knitr)
library(icon)

# Set chunk options
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 10
)
```

```{r prep-url, include=FALSE}
# Generate a link to Wookiepedia for each character
char_data <- filter(starwars_complete, name == params$name) %>% 
  mutate(
    url = paste0(
      "https://starwars.fandom.com/wiki/",
      str_replace(name, " ", "_"
      )
    )
  )
```

```{r prep-plot, include=FALSE}
# Build a plot of mass vs height for each character
char_plot <- starwars_complete %>% 
  ggplot(aes(x = mass, y = height)) +
  geom_point(size = 5, shape = 20, color = "yellow") +
  geom_point(
    aes(x = char_data$mass, y = char_data$height),
    size = 10, shape = 20, color = "red"
  ) +
  labs(x = "Mass (kg)", y = "Height (cm)") +
  theme_classic() +
  theme(
    panel.background = element_rect(fill = "black"),
    plot.background = element_rect(color = "black", fill = "black"),
    text = element_text(family = "LibreFranklin-Light"),
    axis.text = element_text(color = "yellow", size = 15),
    axis.title = element_text(color = "yellow", size = 20),
    axis.title.x = element_text(margin = margin(t = 30, r = 0, b = 0, l = 0)),
    axis.title.y = element_text(margin = margin(t = 0, r = 30, b = 0, l = 0)),
    axis.ticks = element_line(color = "yellow")
  )
```
---
class: middle, center

# `r char_data$name`

### A micro-dossier

<font size=50>`r fa_r_project(colour = "yellow")` `r fa_journal_whills(colour = "yellow")`</font>

Demo of iterative rendering of [{xaringan}](https://slides.yihui.org/xaringan/#1) slides with params using [{purrr}](https://purrr.tidyverse.org/)

[Data source](https://dplyr.tidyverse.org/reference/starwars.html) | [Slide source](https://www.github.com/matt-dray/ninja-knitting/) | [Blog post](https://www.rostrum.blog/2020/03/12/knit-with-params/)

---
class: middle

`r char_data$name`

* is a `r paste(char_data$gender, tolower(char_data$species), "from", char_data$homeworld)`

* has mass `r char_data$mass` kg and height `r char_data$height` cm

* has `r char_data$eye_color` eyes `r ifelse(char_data$hair_color == "none", "", paste("and", str_replace(char_data$hair_color, ", ", "/"), "hair"))`

<br>

Find out more on [Wookiepedia](`r char_data$url`)

---
class: middle

`r paste0(pull(char_data, name), "'s size in context")`

```{r plot}
char_plot
```
